\documentclass[defaultstyle,11pt]{thesis}

\usepackage{adjustbox}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{amsmath}
\usepackage{xspace}

\usepackage[numbers,sort&compress]{natbib}
%\usepackage[utf8]{inputenc}
%\usepackage{bm}% bold math
%\usepackage{tocloft}
%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

%\widowpenalty=9999
%\clubpenalty=9999

%%% Set the numbering down to the subsubsection level (3)                                                                        
\setcounter{secnumdepth}{3}

%%% Similarly set the table of contents numbering down to the                                                                    
%%% subsubsection level (3)                                                                                                      
\setcounter{tocdepth}{3}

%\usepackage[titletoc]{appendix}

\title{Measurement of Elliptic Flow in \pau Collisions at \sqsn = 200 GeV using the PHENIX Detector at RHIC}
\author{Theodore}{Koblesky}
\otherdegrees{B.S., University of Illinois, 2011}
\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D., High Energy Nuclear Physics}		%  #2 {short descr.}
\dept{Department of}			%  #1 {designation}
	{Physics}		%  #2 {name}
\advisor{Professor}				%  #1 {title}
	{James Nagle}			%  #2 {name}
\reader{Professor Dennis Perepelitsa}		%  2nd person to sign thesis

%\frontmatter
%\maketitle
%\makecommitteepage
\input macros.tex


\abstract{\OnePageChapter	% because it is very short	
The Quark Gluon Plasma (QGP), a hot and dense state of matter in which quarks are not confined inside hadrons, is thought to be the same as the matter comprising the entire universe approximately one microsecond after the Big Bang. In \auau collisions at \sqsn = 200 GeV at the Relativistic Heavy Ion Collider (RHIC) and \pbpb collisions at \sqsn = 2.76 TeV at the Large Hadron Collider (LHC), QGP has been discovered to have unique properties, such as its opacity to color charges and the fact that it behaves like a near-perfect fluid. Collective behavior in the form of a substantial elliptical azimuthal anisotropy ($v_2$) in the momentum distribution of final state particles has been observed, indicating a strongly-coupled, hydrodynamically flowing medium. 

Recently, features of collectivity have been detected in high-multiplicity, small collision systems thought to be too small to produce the QGP, such as \hau and \dau at \sqsn = 200 GeV, \ppb at \sqsn = 5 TeV, and in \pp at \sqs = 13 TeV events. In order to constrain models seeking to describe this phenomena, collision systems with distinct initial collision geometries were run at RHIC: \hau for triangular geometry, \dau for elliptical geometry, and \pau for circular geometry. Together with coauthors, in a theory paper published in 2014, we proposed the suite of measurements at RHIC of the three collision systems~\cite{PhysRevLett.113.112301}.

This thesis is the completion of that set of three measurements, by measuring $v_2$ in the \pau system. This thesis gives details on the analysis techniques used to make the measurement including the quality assurance of the data, the optimization of the midrapidity charged hadron cuts, and the event plane angle calibration. Special attention is given to correcting the systematic effects produced by the beam alignment unique to the \pau dataset in order to make the $v_2$ measurement with sufficient precision. Comparisons of $v_2$ in the three collision systems and various theoretical models are made and it appears to be consistent with a QGP being formed. I am a coauthor on the experimental paper with these thesis results which has been published in Physical Review C~\cite{Aidala:2016vgl}.

%In conjunction with the PHENIX group at Vanderbilt, the author produced and analyzed the terabytes of raw data to make the final $v_2$ measurement in the \pau dataset. Unique analysis techniques were necessary to make the first $v_2$ measurement in \pau collisions at \sqsn = 200 GeV. The author spent six months engineering and refining the unique customized weighting used in the event plane analysis method which was necessary in making $v_2$ measurement with sufficient precision.

}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	
	}
	
%\input glossary.tex

\begin{document}

%\IRBprotocol{E927F29.001X}	% optional!

%\ToCisShort	% use this only for 1-page Table of Contents
%\tableofcontents

%\LoFisShort	% use this only for 1-page Table of Figures
 %\emptyLoF	% use this if there is no List of Figures

%\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%         BEGIN DOCUMENT...                                                             %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\mainmatter

\input chapter1.tex
\input chapter2.tex
\input chapter3.tex
\input chapter4.tex
\input chapter5.tex
\input chapter6.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{unsrtnat}	% or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input appendixA.tex
\input appendixB.tex



\end{document}

